Efficient GPU implementation of multicomponent and multiphase Lattice Boltzmann models.

### 2010-04-01 paper.tex
Update my affiliation.
Add zipcode, fix GPUs in abstract, change the paper title.

\begin{document}
%%%%% title : short title may not be used but TITLE is required.
% \title{TITLE}
% \title[short title]{TITLE}
\title{The effecient GPU lattice Boltzmann multicomponent and multiphase systems modelling}

%%%%% author(s) :
% single author:
% \author[name in running head]{AUTHOR\corrauth}
% [name in running head] is NOT OPTIONAL, it is a MUST.
% Use \corrauth to indicate the corresponding author.
% Use \email to provide email address of author.
% \footnote and \thanks are not used in the heading section.
% Another acknowlegments/support of grants, state in Acknowledgments section
% \section*{Acknowledgments}
\author[M.~Januszewski and A.~Kuzmin]{M.~Januszewski\affil{1}\corrauth and A.~Kuzmin\affil{2}}
\address{\affilnum{1}\ University, Poland\\
\affilnum{2}\ Department of Mechanical and Manufacturing Engineering,
Schulich School of Engineering,
University of Calgary, Canada
}
\emails{{\tt michalj@gmail.com} (M.~Januszewski),{\tt shurik.kuzmin@gmail.com} (A.~Kuzmin)}

@@

%%%%% Begin Abstract %%%%%%%%%%%
\begin{abstract}
Despite the number and successful implementations of number of lattice Boltzmann systems on Graphical Processor Units (GPUs), the implementation of more complicated problems as multiphase models or Nearest-Neighbours (NN) interaction, which includes all the boundary conditions, on GPUs is still not well developed. The purpose of the paper is twofold: to develop the efficient GPUs implementation algorithms for the binary liquids flows, which are subclass of the NN interactions, and to illustrate the usefullness in terms of performance of GPUs for multiphase models simulations.
\end{abstract}
%%%%% end %%%%%%%%%%%

>>>>

\begin{document}
%%%%% title : short title may not be used but TITLE is required.
% \title{TITLE}
% \title[short title]{TITLE}
\title{Efficient GPU implementation of multicomponent and multiphase Lattice Boltzmann models.}

%%%%% author(s) :
% single author:
% \author[name in running head]{AUTHOR\corrauth}
% [name in running head] is NOT OPTIONAL, it is a MUST.
% Use \corrauth to indicate the corresponding author.
% Use \email to provide email address of author.
% \footnote and \thanks are not used in the heading section.
% Another acknowlegments/support of grants, state in Acknowledgments section
% \section*{Acknowledgments}
\author[M.~Januszewski and A.~Kuzmin]{M.~Januszewski\affil{1}\corrauth and A.~Kuzmin\affil{2}}
\address{\affilnum{1}\ Institute of Physics, University of Silesia, 40-007 Katowice, Poland\\
\affilnum{2}\ Department of Mechanical and Manufacturing Engineering,
Schulich School of Engineering,
University of Calgary, Canada
}
\emails{{\tt michalj@gmail.com} (M.~Januszewski),{\tt shurik.kuzmin@gmail.com} (A.~Kuzmin)}

@@

%%%%% Begin Abstract %%%%%%%%%%%
\begin{abstract}
Despite the number and successful implementations of number of lattice Boltzmann systems on Graphics Processing Units (GPUs), the implementation of more complicated problems as multiphase models or Nearest-Neighbours (NN) interaction, which includes all the boundary conditions, on GPUs is still not well developed. The purpose of the paper is twofold: to develop the efficient GPUs implementation algorithms for the binary liquids flows, which are subclass of the NN interactions, and to illustrate the usefullness in terms of performance of GPUs for multiphase models simulations.
\end{abstract}
%%%%% end %%%%%%%%%%%
